Flip score characterisation

### 2018-05-24 analysis/analyses/3-metric_characterisation/4-edge_flip.Rmd
rename description

Add SCORPIUS predictions
```{r}
descriptions <- list(description_scorpius())
data <- dyntoy::generate_toy_datasets(c("linear"), num_replicates=1, num_cells=30, num_genes=10) %>% dynutils::extract_row_to_list(1)

results <- map(descriptions, ~.$run_fun(data$counts))

networks_methods <- tibble(topology=map_chr(descriptions, "name"), milestone_network=map(results, "milestone_network"))
```

>>>>

Add SCORPIUS predictions
```{r}
ti_methods <- list(ti_scorpius())
data <- dyntoy::generate_toy_datasets(c("linear"), num_replicates=1, num_cells=30, num_genes=10) %>% dynutils::extract_row_to_list(1)

results <- map(ti_methods, ~.$run_fun(data$counts))

networks_methods <- tibble(topology=map_chr(ti_methods, "name"), milestone_network=map(results, "milestone_network"))
```
